### 2013-02-15 MSteenhagen-CV.tex
Blocked out 'publications'
Added teaching fields, blocked out some talks (now fits on 2 pages again)

\ind 2009--Present. Tutorial Assistant in Philosophy and Psychology.

\ind 2009--Present. Research Assistant in Philosophy.

@@

\ind 2011--2012. Assistant Lecturer, History and Philosophy of Art.

@@

\ind 2011-2012. Teaching Assistant in Philosophy.

\noindent\href{http://www.hku.nl/web/English.htm}{\emph{Utrecht School of Arts} \vspace{0.01in}}

\ind 2008-2009. Assistant Lecturer in Art Theory and Cultural History.

\noindent\href{http://www.uu.nl/faculty/humanities/EN/organisation/departments/departmentofphilosophy/Pages/default.aspx}{\emph{University of Utrecht, Dept. Philosophy} \vspace{0.01in}}

\ind 2007-2008. Teaching Assistant in Aesthetics and Moral Psychology.

@@

\newpage
%% Presentations
\marginhead{{\vskip 0.4em}Talks}
\medskip
\ind 2013. ``Pictures \& perceptual knowledge'' The Ockham Society, Department of Philosophy, University of Oxford.

@@

\ind 2010. ``Photography and dull causation: Response to Atencia-Linares.'' University College London, 2010 Graduate Conference in Philosophy. (Response paper.)

\ind 2010. ``Explaining the Ugly: Disharmony and Unrestrained Cognition in Kant.'' Institute of Philosophy, London-Berkeley Graduate Conference in Philosophy.

@@

\marginhead{{\vskip 0.3em}Publications}
\medskip

\ind  Steenhagen, M. 2010. `Explaining the Ugly,' \emph{Esthetica,} November.

\ind  Steenhagen, M. 2009. `Verwarring over lelijkheid,' \emph{Cimedart,} 39:2.

\ind  Steenhagen, M. 2008. `De keerzijde van liefde,' \emph{Cimedart,} 38:3.

>>>>

\ind 2009--Present. Tutorial Assistant in Philosophy and Psychology\\ (Psychoanalysis, Metaethics, Perception \& epistemology, Descartes).

\ind 2009--Present. Research Assistant in Philosophy\\ (Philosophy of psychology, Clinical methodology, Psychoanalysis)

@@

\ind 2011--2012. Assistant Lecturer, History and Philosophy of Art (Aesthetics)

@@

\ind 2011-2012. Teaching Assistant in Philosophy (Applied Ethics)

% \medskip
% 
% \noindent\href{http://www.hku.nl/web/English.htm}{\emph{Utrecht School of Arts} \vspace{0.01in}}
% 
% \ind 2008-2009. Assistant Lecturer in Art Theory and Cultural History.
% 
% \medskip
% 
% \noindent\href{http://www.uu.nl/faculty/humanities/EN/organisation/departments/departmentofphilosophy/Pages/default.aspx}{\emph{University of Utrecht, Dept. Philosophy} \vspace{0.01in}}
% 
% \ind 2007-2008. Teaching Assistant in Aesthetics and Moral Psychology.

@@

\newpage
%% Presentations
\marginhead{{\vskip 0.4em}Talks (recent)}
\medskip
\ind 2013. ``Pictures \& perceptual knowledge'' The Ockham Society, Department of Philosophy, University of Oxford.

@@

% \ind 2010. ``Photography and dull causation: Response to Atencia-Linares.'' University College London, 2010 Graduate Conference in Philosophy. (Response paper.)
% 
% \ind 2010. ``Explaining the Ugly: Disharmony and Unrestrained Cognition in Kant.'' Institute of Philosophy, London-Berkeley Graduate Conference in Philosophy.

@@

% \marginhead{{\vskip 0.3em}Publications}
% \medskip
% 
% \ind  Steenhagen, M. 2010. `Explaining the Ugly,' \emph{Esthetica,} November.
% 
% \ind  Steenhagen, M. 2009. `Verwarring over lelijkheid,' \emph{Cimedart,} 39:2.
% 
% \ind  Steenhagen, M. 2008. `De keerzijde van liefde,' \emph{Cimedart,} 38:3.
% 
% \bigskip
